Distance Sampling in \proglang{R}

### 2016-03-18 paper.Rmd
Fix x-axis ticks in Figure 1
#39

set.cex  = 1
set.cex.lab = 1.2
set.cex.main = 2
#Line transect example
plot(x, y, xlab = "Perpendicular distance", ylab = "Probability of detection", type = "l", ylim = c(0,1.1), xaxp = c(0,1,5), cex = set.cex, cex.lab = set.cex.lab)
line.availability <- rep(1,100)
plot(x, line.availability, xlab = "Perpendicular distance", ylab = "pdf of object distances", type = "l", ylim = c(0,1.1), xlim = c(0,500), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab, main = "Line Transect", cex.main = set.cex.main)
plot(x,y, xlab = "Perpendicular distance", ylab= "pdf of observed distances", type = "l", ylim = c(0,1.1), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab)

#Point Transect example
plot(x, y, xlab = "Radial distance", ylab = "Probability of detection", type = "l", ylim = c(0,1.1), xaxp = c(0,1,5), cex = set.cex, cex.lab = set.cex.lab)
point.availability <- 2*pi*x
plot(x, point.availability, xlab = "Radial distance", ylab = "pdf of object distances", type = "l", ylim = c(0,3300), xlim = c(0,500), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab, main = "Point Transect", cex.main = set.cex.main)
point.observed <- y*point.availability
plot(x, point.observed, xlab = "Radial distance", ylab= "pdf of observed distances", type = "l", ylim = c(0,800), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab)

>>>>

set.cex  = 1
set.cex.lab = 1.2
set.cex.main = 2
#Line transect example
plot(x, y, xlab = "Perpendicular distance", ylab = "Probability of detection", type = "l", ylim = c(0,1.1), cex = set.cex, cex.lab = set.cex.lab)
line.availability <- rep(1,100)
plot(x, line.availability, xlab = "Perpendicular distance", ylab = "pdf of object distances", type = "l", ylim = c(0,1.1), xlim = c(0,500), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab, main = "Line Transect", cex.main = set.cex.main)
plot(x,y, xlab = "Perpendicular distance", ylab= "pdf of observed distances", type = "l", ylim = c(0,1.1), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab)

#Point Transect example
plot(x, y, xlab = "Radial distance", ylab = "Probability of detection", type = "l", ylim = c(0,1.1), cex = set.cex, cex.lab = set.cex.lab)
point.availability <- 2*pi*x
plot(x, point.availability, xlab = "Radial distance", ylab = "pdf of object distances", type = "l", ylim = c(0,3300), xlim = c(0,500), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab, main = "Point Transect", cex.main = set.cex.main)
point.observed <- y*point.availability
plot(x, point.observed, xlab = "Radial distance", ylab= "pdf of observed distances", type = "l", ylim = c(0,800), yaxt = "n", cex = set.cex, cex.lab = set.cex.lab)
